Re-finding to support a Deep Web Question Answering System

### 2010-03-04 paper/semsearch10/content/example.tex
third round of changes by jnw

@@

Each answer to a question is created using a {\it query response
  method} (QRM). A QRM is constructed when a special user, known as a
{\it guide} answers a question using an instrumented web browser (the
{\it query response recorder} or QRR) that records web
interactions. The system extracts the relevant artifacts of the
guide's actions and stores them in the QRM. The QRM is characterized
by a {\it semi-structured query} (SSQ), a schematic representation of
the information contained in the query, namely the inputs and output
contexts---the {\it who, what, when,} and {\it where}
categories---that characterize the question together with an
appropriately generalized representation of the guide's browser
interactions.  The {\it query response evaluator} (QRE) evaluates a
query by binding specific arguments to its input parameters and
replaying the generalized web interactions the guide used to answer
the original question.

>>>>

%jnw

@@

Each answer to a question is created using a \emph{query response
  method} (QRM). A QRM is constructed when a special user, known as a
\emph{guide} answers a question using an instrumented web browser (the
\emph{query response recorder} or QRR) that records web
interactions. The system extracts the relevant artifacts of the
guide's actions and stores them in the QRM. The QRM is characterized
by a \emph{semi-structured query} (SSQ), a schematic representation of
the information contained in the query, namely the inputs and output
contexts---the \emph{who, what, when,} and \emph{where}
categories---that characterize the question together with an
appropriately generalized representation of the guide's browser
interactions.  The \emph{query response evaluator} (QRE) evaluates a
query by binding specific arguments to its input parameters and
replaying the generalized web interactions the guide used to answer
the original question.

### 2010-03-04 paper/semsearch10/content/introduction.tex
third round of changes by jnw

\section{Introduction}
% Christan
When traveling though a jungle to a destination, it is easy to get lost.  If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.  However, if you are the \emph{n}th person to take a path, you may be able to follow the path that was left by the \emph{n-1} other people to walk the path.  An article by Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.  We use this insight to to improve the efficency of retrieval in semantic search.

Instead of treating each user search as a unique search, it is beneficial to assume that a similar search has been previously performed.  Researchers have shown that almost 40 percent of the all queries are repeats \cite{1277770}.  This means there is a large open area for optimization for search engines.  We have built a prototype system for deep web question answering that uses previously answered questions to obtain new answers.

In this paper we describe a system for recording the answer to user queries and executing solutions to similar queries.  To support this we use a structured query representation.  The structured representation allows queries to be parameterized so that similar queries may be discovered at query-time.  To recognizing these queries we build a semantic heterarchy and define algorithms for matching the classes.

The paper proceeds as follows:
\begin{itemize}
\item Discussion of the query structure.  We call this structure an \emph{semi-structured query} SSQ.
\item Next we discuss how we create the class heterarchy to support the semantic comparisons.
\item In section \ref{sec:Building Query Store} we discuss how we record user web queries and correctly annotate them.
\item Next, we discribe how we match rank 
\item ....
\item We will conclude by discussing the examples of the system.
\end{itemize}

>>>>

\section{Introduction}
% Christan
When traveling though a jungle to a destination, it is easy to get
lost.  The first person to go somewhere may make a number of mistakes
in trying to find the best path to their destination.  However, those
who come later will find it easy to reach that destination if a
well-marked trail without the has been created. Olsen and Malizia
describe this idea as \emph{exploiting trails} \cite{5379671}.  Rather
than treating each user's search as a unique entity and working from
first principles, one can exploit the fact that a similar search may
have been performed already.  In one study, almost 40 percent of all
queries were found to be repetitions of previous
queries.\cite{1277770} This points to way to optimize the search
process.  We have built a prototype system for answering questions
using deep-web sources that employs previously answered questions to
obtain new answers.  Using our analogy, the Morpheus question
answering system follows path-finders to their destinations and not
only marks the trail, but provides a taxi service to take followers to
similar destinations.

### 2010-03-04 paper/semsearch10/content/query_reexecution.tex
third round of changes by jnw

\subsection{Query Re-execution}
% Chris
	I ASSUME CLINT HAS COVERED QRM SELECTION ALREADY
	When a user submits a new query to the Morpheus system, one or more stored 
Query Resolution Methods are executed to obtain results. A QRM consists of an XML script which instructs the Query Resolution Executor how to obtain the required result. The Query Resolution Executor may "click" links, submit forms or highlight and save important pieces of html, including answers. At the present, the GET form submission method is used. 
	There is greater complexity in dealing with web forms than with links. For a given
form, there may be text fields, drop-down boxes, radio buttons etc. In order to support form submission in such circumstances the QRE will take different actions based on the input type. For text fields, simply adding a key/value pair to the querystring suffices. For a drop-down box, the QRE extracts the form element and performs a lookup on its options to find the appropriate value to include in the querystring. 
	All input data as well as highlighted HTML is kept in an internal hash table. The QRM script contains keys which allow the QRE to map SSQ inputs from the table to the appropriate form inputs. Furthermore, highlights which are collected during execution are stored in the hash table. 
	Once all pages included in the script have been visited, the QRE returns the HTML snippet containing the answer. This answer can then be rendered in a browser. Normally a list of QRMs, sorted by relevance, are given to the QRE. Therefore after execution a list of results is returned in order of relevance.

>>>>

\subsection{Query Re-execution}
% Chris
When a user submits a new query to the Morpheus system, one or more
stored Query Resolution Methods are executed to obtain results. A QRM
consists of an XML script which instructs the Query Resolution
Executor how to obtain the required result. The Query Resolution
Executor may "click" links, submit forms or highlight and save
important pieces of html, including answers. At the present, the GET
form submission method is used.  There is greater complexity in
dealing with web forms than with links. For a given form, there may be
text fields, drop-down boxes, radio buttons etc. In order to support
form submission in such circumstances the QRE will take different
actions based on the input type. For text fields, simply adding a
key/value pair to the querystring suffices. For a drop-down box, the
QRE extracts the form element and performs a lookup on its options to
find the appropriate value to include in the querystring.  All input
data as well as highlighted HTML is kept in an internal hash
table. The QRM script contains keys which allow the QRE to map SSQ
inputs from the table to the appropriate form inputs. Furthermore,
highlights which are collected during execution are stored in the hash
table.  Once all pages included in the script have been visited, the
QRE returns the HTML snippet containing the answer. This answer can
then be rendered in a browser. Normally a list of QRMs, sorted by
relevance, are given to the QRE. Therefore after execution a list of
results is returned in order of relevance.

### 2010-03-04 paper/semsearch10/content/ssq_ranking.tex
third round of changes by jnw

\subsection{SSQ Ranking}
In order to match a new query with a SSQ within our data store, we have defined similarity measures between the ontologies of the new query and the candidate SSQs. These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs. The similarity measures are implemented in two scenarios: \textit{on-line execution} and \textit{off-line mode}. The \textit{on-line execution} is time sensitive and is used primarily for relating newly defined SSQs to the SSQs in the store. During \textit{off-line execution}, the system clusters similar SSQs.

>>>>

\subsection{SSQ Ranking}
\label{sec:ssq}
In order to match a new query with a SSQ within our data store, we
have defined similarity measures between the ontologies of the new
query and the candidate SSQs. These measures capture the distance
between the ontology classes, properties, and individuals at the
conceptual level in addition to simply matching URIs. The similarity
measures are implemented in two scenarios: \textit{on-line execution}
and \textit{off-line mode}. The \textit{on-line execution} is time
sensitive and is used primarily for relating newly defined SSQs to the
SSQs in the store. During \textit{off-line execution}, the system
clusters similar SSQs.
